---
title: "p8105_hw1_tlm2152"
author: "Tucker Morgan"
date: "9/29/2021"
output: github_document
---

```{r setup}
library(tidyverse)
```

## Problem 1
```{r}
set.seed(1)

prob1_df <- tibble(
  ran_sample = rnorm(10),
  greater_than_0 = ran_sample > 0,
  vec_char = c("well", "plug", "me", "in", "just", "like", "I", "was", "Eddie", "Harris"),
  vec_factor = factor(c("Ad-Rock", "MCA", "Mike D", "MCA", "MCA", "Ad-Rock", "MCA", "Mike D", "Mike D", "MCA"))
)
```
Above, I've created a data frame with four vectors:

* a random sample of size 10 from a standard Normal distribution;
* a logical vector that indicates if the sample is greater or less than 0;
* a character vector of length 10 with the opening lyrics from So What'cha Want by the Beastie Boys;
* a factor vector with three levels, each level a name of a member of the Beastie Boys.

I will now try to take the mean of each variable in the data frame.
```{r}
ran_sample_mean <- mean(pull(prob1_df, "ran_sample"))
greater_than_0_mean <- mean(pull(prob1_df, "greater_than_0"))
vec_char_mean <- mean(pull(prob1_df, "vec_char"))
vec_factor_mean <- mean(pull(prob1_df, "vec_factor"))
```
The means were attainable for the random sample vector and the logical vector. The mean of the character and factor vectors could not be found since they are neither numberic nor logical. The mean of the random sample is `r ran_sample_mean` and the mean of the logical vector is `r greater_than_0_mean`.

I will now attempt to convert the logical, character, and factor vectors to numeric vectors using `as.numeric`.
```{r, eval = FALSE}
as.numeric(pull(prob1_df, "greater_than_0"))
as.numeric(pull(prob1_df, "vec_char"))
as.numeric(pull(prob1_df, "vec_factor"))
```
When I run each line of code, I find that R converts the logical vector into numbers where TRUE = 1 and FALSE = 0. This makes sense as the logical vector returns only two values. However, the character vector is converted to NAs for each entry. It doesn't make much sense for R to convert these words to numbers, since they don't have as clear of a numeric meaning as TRUE / FALSE. That explains why I could find the mean of the logical vector but not the character vector above.

The factor vector entries are converted into 1, 2, or 3 depending on factor level. I can even find the mean of this numeric vector to be `r mean(as.numeric(pull(prob1_df, "vec_factor")))`. One could infer that this means "MCA" (level 2) and "Mike D" (level 3) appear more frequently in this list, but a frequency table may be more informative in this case.


## Problem 2
I'll start by loading the `penguins` data set.
```{r}
data("penguins", package = "palmerpenguins")
penguins
```
This data set contains info on `r nrow(penguins)` sample penguins for `r ncol(penguins)` attributes: `r names(penguins)`. Penguins are classified as 1 of 3 species - `r levels(pull(penguins, species))` - and from 1 of 3 islands - `r levels(pull(penguins, island))`. Bill length can range from `r min(pull(penguins, bill_length_mm), na.rm = TRUE)`mm to `r max(pull(penguins, bill_length_mm), na.rm = TRUE)`mm, while bill depth can range from `r min(pull(penguins, bill_depth_mm), na.rm = TRUE)`mm to `r max(pull(penguins, bill_depth_mm), na.rm = TRUE)`mm. Flipper length ranges from `r min(pull(penguins, flipper_length_mm), na.rm = TRUE)`mm to `r max(pull(penguins, flipper_length_mm), na.rm = TRUE)`mm with a mean of `r round(mean(pull(penguins, flipper_length_mm), na.rm = TRUE),2)`mm.
